Ants-Review: A Protocol For Open Anonymous Peer-Reviews

### 2020-07-10 paper-v1.tex
cleanup by @naszam

///@title Ants-Review
///@author Nazzareno Massari
///@notice ANTS ERC20 Token
///@dev All function calls are currently implemented without side effects through TDD approach
///@dev OpenZeppelin library is used for secure contract development

>>>>

///@title Ants-Review
///@author Nazzareno Massari
///@notice Ants-Review ERC20 Token
///@dev All function calls are currently implemented without side effects through TDD approach
///@dev OpenZeppelin library is used for secure contract development
